---
title: "p8105_hw5_jz3180"
author: "Jinghan Zhang"
date: "11/15/2020"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```


## Problem 1

Read in the data.

```{r}
homicide_df = 
  read_csv("./homicide_data/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```

Looking at the data:

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```


```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```


## Problem 2

```{r import and spaghetti plot, error = TRUE}
path_df = 
  tibble(
    path = list.files("lda_data"),
  ) %>% 
  mutate(
    path = str_c("lda_data/", path),
    data = map(path, read_csv)
    ) %>% 
  unnest(data) %>% 
  separate(
    path,
    into = c(NA, NA, "arm", "subj", NA)
  ) %>%
  pivot_longer(
    starts_with("week"),
    names_to = "week",
    values_to = "values"
  ) %>%
  mutate(
    week = as.numeric(sub("week_", "", week))
  )

experiment_df = path_df %>% filter(arm == "exp")
control_df = path_df %>% filter(arm == "con")

spaghetti = ggplot(control_df, aes(x = week, y = values, group = subj)) + geom_line() + geom_line(data = experiment_df, color = "red")
spaghetti + labs(y = "Observations", x = "Week", title = "Observations on each Subject Over Time")
```

From the plot, the general trend of control arm subjects seem to have stable observation values over time (period of weeks). On the other hand, the experimental arm subjects generally seem to trend upwards in throughout the course of the obervational time.

## Problem 3

```{r simulation}

ttest_sim = function(sample_size = 30, mu, sigma = 5)
{
  input_sim = tibble(
    x = rnorm(n = sample_size, mean = mu, sd = sigma)
  ) %>%
    t.test() %>%
    broom::tidy()
}

first_sim = 
  rerun(5000, ttest_sim(mu = 0)) %>% 
  bind_rows()

data_sim = 
  tibble(
  mu = c(0, 1, 2, 3, 4, 5, 6)
  ) %>% 
  mutate(
    outputs = map(.x = mu, ~ rerun(5000, ttest_sim(mu = .x))),
    results = map(outputs, bind_rows)
  ) %>% 
  select(-outputs) %>%
  unnest(results) %>% 
  select(mu, estimate, p.value) %>% 
  mutate(
    rejected = case_when(
      p.value <= 0.05 ~ "yes",
      p.value > 0.05  ~ "no"
      ))
```


```{r plot one, message = FALSE, warning = FALSE}
prop_reject = 
  data_sim %>% 
  group_by(mu, rejected) %>% filter(rejected == "yes") %>% 
  summarise(
    total = n()) %>% 
  mutate(
    proportion = total / 5000
  ) 
prop_reject %>% 
   ggplot(aes(x = mu, y = proportion)) +
  geom_point() + geom_smooth() +
  labs(y = "Proportion of Rejected Null", x = "True Value of Mu", title = "Power of Test vs. True Value of Mu")
```


```{r plot two, message = FALSE, warning = FALSE}
avg_mu = 
  data_sim %>%
  group_by(mu) %>%
  summarize(
    avg = mean(estimate)
  ) 
avg_mu %>% 
  ggplot(aes(x = mu, y = avg)) +
  geom_point() + geom_smooth(method=lm) +
  labs(y = "Average Estimate of Mu", x = "True Value of Mu", title = "Average of Mu vs. True Value of Mu")
```


```{r plot three, message = FALSE, warning = FALSE}
avg_mu_reject = 
  data_sim %>%
  group_by(mu) %>%
  filter(rejected == "yes") %>% 
  summarize(
    avg_mu_reject = mean(estimate)) 
avg_mu_reject %>% 
  ggplot(aes(x = mu, y = avg_mu_reject)) +
  geom_point() + geom_smooth(method = lm) +
  labs(y = "Average Estimate of Mu (Rejected)", x = "True Value of Mu", title = "Average of Mu for Rejected Nulls vs. True Value of Mu")
```
